Corpus Analysis

### 2020-08-27 inst/analysis/corpus-stage2.Rmd
Added programs counting

>>>>

### Programs

```{r}
package_runs <- trace_runs_raw %>%
  mutate(
    dir=as.character(path("../../run/package-evals-traced", package, basename(file))),
    file=as.character(path("./", basename(dirname(file)), basename(file))),
  ) %>%
  semi_join(corpus, by="package")

package_programs <-
  left_join(
    filter(package_runs, exitval==0) %>% select(package, file, dir, time), 
    runnable_code_raw %>% select(package, file=filename, code),
    by=c("package", "file")
  ) %>%
  filter(!endsWith(file, "tests/testthat.R"), !endsWith(file, "tests/run-all.R")) %>% # testthat drivers are not traced
  transmute(
    type=basename(dirname(file)),
    file=as.character(path(dir, "calls.fst")),
    code, 
    runtime=time,
    corpus="cran"
  )

package_programs_errors <- 
  package_programs %>%
  mutate(
    error_file=path(dirname(str_replace(file, fixed("../.."), params$base_dir)), "calls-ERROR"), 
    error=file.exists(error_file)
  ) %>%
  filter(error) %>%
  rowwise() %>%
  do(mutate(read_fst(.$error_file), file=.$file))

package_programs <-
  left_join(
    package_programs, 
    transmute(package_programs_errors, error=paste(source, message, call), file), 
    by="file"
  ) %>%
  mutate(
    success=
      type %in% c("examples", "tests", "vignettes") & 
      !is.na(code) &
      !is.na(runtime) &
      code > 0 &
      is.na(error)
  )
```

```{r}
write_fst(package_programs, CRAN_PROGRAMS_FILE)
```
